---
title: "Analysis for Vasilyeva"
output: html_document
date: "2024-01-23"
---

```{r setup, include=FALSE}
library(tidyverse)
library(here)
library(jsonlite)

raw_data_loc <- "vasilyeva_2018/data/"
raw_raw <- read_csv(here(raw_data_loc, "raw_full.csv")) %>% 
  filter(StartDate!="Start Date") %>% 
  filter(!str_detect(StartDate, "ImportId")) %>% 
  select(-Status, -IPAddress, -Progress, -Finished, -starts_with("Recipient"),
         -ExternalReference, -starts_with("Location"), -DistributionChannel, -UserLanguage,
         -`prolific-id`, -PROLIFIC_PID) %>% 
  mutate(StartDate=as.Date(StartDate)) %>% 
  filter(StartDate > as.Date("2024-02-21")) %>% 
  write_csv(here(raw_data_loc,"anon_full.csv"))
```

```{r data cleaning, include=T}
raw_dat <- read_csv(here(raw_data_loc, "anon_full.csv"), col_types=cols(.default="c"))
#### Data exclusion / filtering

data <- raw_dat %>% 
  mutate(id = row_number()) %>% #create id row and bring it to the front
  select(id, everything()) %>% 
  filter(Consent == "2") %>% #consenting
  # filter(Mch.z1 == 1,
  #        Mch.z2 == 1,
  #        Mch.d1 == 1,
  #        Mch.d2 == 1,
  #        Mch.g1 == 1,
  #        Mch.g2 == 1,
  #        Mch.y1 == 1,
  #        Mch.y2 == 1) %>% #check questions
  select(-starts_with(c( #getting rid of irrelevant columns, including check questions
                        "prolific-id",
                        "PROLIFIC_PID",
                        "StartDate",
                        "Duration",
                        "EndDate",
                        "RecordedDate",
                        "Consent",
                        "ResponseId",
                        "tableorder",
                        "cov"))) %>% 
  pivot_longer(!c(id, task, moderator, starts_with("Comm"), Age, Gender), names_to = "question_type", values_to = "rating") %>%  #turn table into longer
  mutate(presence_of_moderator = case_when(moderator == "drolyuyu" & grepl("d3", question_type) ~ "present", #create column indicating whether it was moderated or not
         moderator == "drolyuyu" & grepl("d4", question_type) ~ "present",
         moderator == "drolyuyu" & grepl("y3", question_type) ~ "present",
         moderator == "drolyuyu" & grepl("y4", question_type) ~ "present",
         moderator == "zelmogrimond" & grepl("z3", question_type) ~ "present",
         moderator == "zelmogrimond" & grepl("z4", question_type) ~ "present",
         moderator == "zelmogrimond" & grepl("Z3", question_type) ~ "present",
         moderator == "zelmogrimond" & grepl("Z4", question_type) ~ "present",
         moderator == "zelmogrimond" & grepl("g3", question_type) ~ "present",
         moderator == "zelmogrimond" & grepl("g4", question_type) ~ "present",
         TRUE ~ "absent")) %>% 
  mutate("causalexplanatoryCF" = case_when(grepl("CaTy", question_type) ~ "causal", #change column names
                                     grepl("ExTy", question_type) ~ "explanatory",
                                     grepl("CaTo", question_type) ~ "causal",
                                     grepl("ExTo", question_type) ~ "explanatory",
                                     grepl("Ty.CF", question_type) ~ "counterfactual",
                                     grepl("To.CF", question_type) ~ "counterfactual")) %>% 
  mutate("typetoken" = case_when(grepl("CaTy", question_type) ~ "type", #change column names
                                     grepl("ExTy", question_type) ~ "type",
                                     grepl("CaTo", question_type) ~ "token",
                                     grepl("ExTo", question_type) ~ "token",
                                     grepl("Ty.CF", question_type) ~ "type",
                                     grepl("To.CF", question_type) ~ "token")) %>% 
    mutate(rating=as.numeric(rating))

data %>% write_csv(here(raw_data_loc, "full_data.csv"))
```


```{r}
#package installation
#don't forget Hmisc!
#source data

theme_set(theme_bw())
```

Data explanation:
* id is a participant id number
* CommOwn, Comments, Age, Gender are by-participant how they answered some demographic questions at the end
* question_type starting with Mch is the check questions at the end -- the correct answer is always 1
* rating is the 1-7 rating
* presence_of_moderator is whether there was a moderator or not
* causalexplanatoryCF is what the dependent measure was (causal/explanatory/counterfactual)
* typetoken is type or token


Data clean up:

For the purposes of pilot analysis we should write the code that will do the filtering and check that it works
but for the goodness of the rest of the code, we'll keep in the junk data just to have more points to work with!

```{r}

# how many participants total
data %>% distinct(id) %>% nrow()

#make a data frame of participants who correctly answered all Mch questions
# we do this by filtering for only the correct answers
# and then checking if there are 8 rows / person (8 questions)
all_correct <- data %>% filter(str_detect(question_type, "Mch")) %>% 
  filter(rating==1) %>% 
  group_by(id) %>% 
  summarize(count=n()) %>% 
  filter(count==8)

# how many participants kept in?
all_correct %>% nrow()
  

data_filtered <- data %>% #inner_join(all_correct) %>% # you will want this in the real data, but to have both explanatory & causal include all the data for now
  filter(!str_detect(question_type, "Mch")) %>% #get rid of comp checks now
  filter(!is.na(rating))

#confirm filter
data_filtered %>% distinct(id) %>% nrow()

```

From paper, "Experiment 1 had a 2 moderator (moderated vs. non-moderated relationship) x 2 judgment (causal vs. explanatory) x 2 target (type vs. token) mixed design, with moderator manipulated within-subjects. The dependent variables were agreement with causal or explanatory claims, and agreement with counterfactual claims, measured on a 1 (strongly disagree) to 7 (strongly agree) scale."

From paper " 2 moderator (moderated relationship, non-moderated relationship) x 2 judgment (causal,
explanatory) x 2 target (type, token) mixed ANOVA on causal and explanatory ratings
revealed a main effect of moderator: as shown in Fig. 2a, participants were significantly
less likely to agree with claims about causal and explanatory relationships when a rela-
tionship was moderated than non-moderated, F(1, 178) = 163.22, p < .001 [...]
even though moderated and non-moderated relationships were equated for overall strength
(defined as the degree of covariation between putative causes and effects)."

```{r}
# use ggplot to make a plot visualizing your data 
# in a way that could be compared to Fig 2 in the paper

data_filtered %>% filter(causalexplanatoryCF %in% c("explanatory", "causal")) %>% 
  ggplot(aes(x=presence_of_moderator, y=rating))+geom_jitter(width=.1, height=0)+
  stat_summary(fun.data="mean_cl_boot")+#mean + bootstrapped 95% CIs
  coord_cartesian(ylim=c(1,7))+
  facet_grid(typetoken~causalexplanatoryCF)

```

```{r}
# run a linear model of the threeway interaction 
mod <- lm(rating ~ presence_of_moderator * typetoken * causalexplanatoryCF, data=data_filtered %>% filter(causalexplanatoryCF %in% c("explanatory", "causal")))

summary(mod)
```
The counterfactual ratings showed a similar pattern: a 2 moderator (moderated relation-
ship, non-moderated relationship) x 2 target (type, token) mixed ANOVA on counterfactual
ratings showed a main effect of moderator

```{r}
# do a counterfactual graph

```

```{r}
# run a counterfactual linear model 
