---
title: "Analysis for Atir2015"
output: html_document
date: "2024-01-23"
---

```{r setup, include=FALSE}
library(tidyverse)
library(here)
library(jsonlite)


dat_loc <- "sheppes_2011/data"
raw <- read_csv(here(dat_loc, "pilot_B.csv")) |> 
  select(-starts_with("failed"), -proliferate.condition, -internal_node_id, -error)

raw2 <- read_csv(here(dat_loc, "pilot_A.csv")) |> 
  select(-starts_with("failed"), -proliferate.condition, -internal_node_id, -error)

processed <- raw  |> group_by(workerid) |> 
    filter(grepl("l.jpg|l.JPG|h.jpg|h.JPG", stimulus)) |>
  filter(grepl("image-button-response", trial_type)) |>
  mutate(intensity = ifelse(grepl('l.jpg|l.JPG', stimulus), 'low', 'high'),
         approach=case_when(
           response=="0" ~ "reappraise",
           response=="1" ~ "distract",
           T ~ NA
         )) |> 
  select(workerid, intensity, approach, rt, stimulus, trial_index) |> write_csv(here(dat_loc, "pilot_data.csv"))
  
```


From text "Figure 2a shows that participants chose to employ reappraisal
on 76.3% of the low-intensity trials (95% confidence interval,
or CI: [66.3, 86.3]), but chose to employ distraction on 70.7%
of the high-intensity trials (95% CI: [60.7, 80.7]), F(1, 19) =
47.54, p < .000001, ηp2 = .71. This bias in regulatory decision
making was observed in 90% (18/20) of the participants.
These findings provide clear support for our hypothesis."

```{r}
# how many participants
processed |> distinct(workerid) |> nrow()


# calculate per participant ratios
per_participant <- processed |> group_by(workerid, intensity) |> 
  summarize(reappraise_rate=sum(approach=="reappraise")/n())

```

```{r}
#plot the rates of reappraisal for low and high intensity

ggplot(per_participant, aes(x=intensity, y=reappraise_rate))+geom_point()
```
```{r}
#run a binomial glm predicting using reappraisal as a function of intensity
for_mod <- processed |> mutate(is_reappraisal=ifelse(approach=="reappraise", 1,0))

mod <- glm(is_reappraisal ~ intensity, data=for_mod, family="binomial")
summary(mod)
```

```{r}
# run the ANOVA / F-test 
```
