---
title: "Analysis for Atir2015"
output: html_document
date: "2024-01-23"
---

```{r setup, include=FALSE}
library(tidyverse)
library(here)
library(jsonlite)


dat_loc <- "long_2017/data"
raw <- read_csv(here(dat_loc, "full_sample.csv")) #%>% bind_rows(read_csv(here(dat_loc, "pilot_B.csv")))


processed <- raw %>% group_by(workerid) %>% 
  mutate(is_practice=case_when(
    str_detect(stimulus, "Practice")~"practice",
    str_detect(stimulus,"Block")~"critical",
    T  ~ NA)) %>% 
  fill(is_practice) %>% 
  filter(!is.na(ask)) %>% 
  select(workerid, is_practice, ask, type, correct, rt, left, right, response, trial_index) |> write_csv(here(dat_loc, "full_data.csv"))
  
```

Data description:
* workerid is a per-participant id
* is_practice is either practice or critical
* ask is big or small (for whether they were asked to select the bigger or smaller)
* type is congruent or incongruent
* correct is whether their answer was correct
* rt is reaction time

```{r}
# exclude practice trials

# exclude incorrect answers

# exclude rt < 200ms and > 1500 ms

filtered <- processed %>% filter(is_practice!="practice") %>% 
  filter(correct) %>% 
  filter(rt>200) %>% 
  filter(rt<1500)

filtered %>% distinct(workerid) %>% nrow()
```

```{r}
#plot the relationship between condtion and RT

ggplot(filtered, aes(x=type, y=rt))+
  geom_jitter(width=.1, alpha=.1)+
  stat_summary(fun.data="mean_cl_boot")+
  facet_wrap(~ask)

```

```{r}
# run a linear model predicting RT as a function of conguency, bigger/smaller, and their interaction
mod1 <- lm(rt~type*ask, data=filtered)
summary(mod1)
```

Per paper "Trimmed reaction times
were analyzed using a 2 x 2 repeated-measures ANOVA, with con-
gruency (congruent/incongruent) and task (bigger/smaller on the
screen) as factors."

```{r}
# run a 2x2 anova with congruency and task (bigger/smaller)
# library(rstatix)
# 
# test_anova <- anova_test(
#   data=filtered, dv=rt, wid=workerid,
#   within=c(type, ask))
# 
# get_anova_table(test_anova)
# )
```