---
title: "Analysis for Atir2015"
output: html_document
date: "2024-01-23"
---

```{r setup, include=FALSE}
library(tidyverse)
library(here)
library(jsonlite)

ParseJSONColumn <- function(x) {
 str_replace_all(x,"'",'"') %>% 
    str_replace_all( 'Don"t know', "Don't know") %>% 
    fromJSON(flatten = T)
}
dat_loc <- "atir_2015/data"
raw <- read_csv(here(dat_loc, "full_sample.csv")) #%>% bind_rows(read_csv(here(dat_loc, "pilot_A.csv")))


processed <- raw %>% group_by(workerid) %>% 
  filter(type %in% c("finance term", "self-rating", "FLquiz"))

#self-perceived knowledge
self_rating <- processed %>% filter(type=="self-rating") %>% 
  mutate(question=ifelse(str_sub(stimulus,1,5)=="<p>In", "generalKnowledge", "compareAmerican")) %>% 
  select(workerid, response, rt, stimulus, trial_index, type, question)

# fake finance terms
finance_terms <- processed %>% filter(type=="finance term") %>% 
  mutate(question=str_sub(stimulus, 4,-9)) %>% 
  select(workerid, response, rt, stimulus, trial_index, type, question)
  
# quiz

quiz <- processed %>% filter(type=="FLquiz") %>% 
  mutate(response=map(response, ParseJSONColumn)) %>% 
  unnest(response) %>% 
  mutate(question=names(response)) %>% unnest(response) %>% 
    select(workerid, response, rt, stimulus, trial_index, type, question)

all <- finance_terms %>% bind_rows(self_rating) %>% bind_rows(quiz) %>% arrange(workerid) %>% 
  select(workerid, type, question, response, everything()) %>% write_csv(here(dat_loc, "full_data.csv"))
```

Data description:
* workerid is a participant id
* type is finance term, FLQuiz, or self-rating
* question is the specific type of question it was 
* response is the response
* rt is reaction time
* stimulus is what the participant saw (Due to the formatting of the experiment, the finance quiz doesn't have the stimuli labels as it was counted as all one question. https://osf.io/fq6vg has the full text for the finance quiz. )
* trial_index is the order items were shown to the participant 


```{r}
grade_quiz <- function(question, response){
  
  grade_line <- function(question, response){
      if (question=="savingsAccount" && response=="More than $102") {return(1)}
      if (question=="inflation" && response=="Less") {return(1)}
      if (question=="interest" && response=="Fall") {return(1)}
      if (question=="mortgage" && response=="True") {return(1)}
      if (question=="stocks" && response=="False") {return(1)}
  else {return(0)}
  }
  
  map2(question, response, grade_line) %>% unlist()
}

fake <- c("pre-rated stocks", "fixed-rate deduction", "annualized credit")

raw_data <- all 

# calculate the overclaim rate for each person
overclaim_score <- raw_data %>% 
  filter(type=="finance term") %>%
  filter(question %in% fake) %>% # we want just the finance term ratings for the fake terms 
  # we want "we computed the proportion of foils rated as 2 or higher, the proportion of foils rated as 3 or higher, and so on for 4, 5, 6, and 7, and then averaged these proportions"
  #mathematically, this is the same as subtracting 1, averaging, and dividing by 6
  mutate(response=as.numeric(response),
         response=response-1) %>% 
  group_by(workerid) %>% 
  summarize(overclaim=mean(response)/6)

# compute an average measure of self-perceived knowledge for each participant
self_rating <- raw_data %>% 
  filter(type=="self-rating") %>% 
  group_by(workerid) %>% 
  mutate(response=as.numeric(response)) %>% 
  summarize(self_rating=mean(response))

# score the quiz
quiz <- raw_data %>% 
  filter(type=="FLquiz") %>% 
  mutate(correct=grade_quiz(question,response)) %>% 
  group_by(workerid) %>% 
  summarize(quiz_score=sum(correct))

# join into 1 row per person

combined <- overclaim_score %>% left_join(self_rating, by="workerid") %>% 
  left_join(quiz, by="workerid")

```

```{r}
# how many participants?
combined %>% distinct(workerid) %>% nrow()

```

```{r}
# graph the relationship between overclaiming and self-perceived knowledge
#with self-rating on the x-axis and overclaim on the y-axis

ggplot(combined, aes(x=self_rating, y=overclaim))+
  geom_point()+
  geom_smooth(method="lm")+
  coord_cartesian(ylim=c(0,1))


# run a linear model predicting overclaiming from quiz scores

ggplot(combined, aes(x=quiz_score, y=overclaim))+
  geom_point()+
  geom_smooth(method="lm")+
  coord_cartesian(ylim=c(0,1))

```

```{r}

# run a linear model predicting overclaiming from self-perceived knowledge

mod1 <- lm(overclaim ~ self_rating, combined)


# what is the correlation between self-perceived knowledge and quiz score?
cor.test(combined$self_rating, combined$quiz_score)
# run a model with both quiz score & self-perceived as predictors
mod_both <- lm(overclaim ~ self_rating + quiz_score, combined)

summary(mod_both)

```

